---
title: "ms_5"
author: "Rachel Phan"
date: "3/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(readr)
library(readxl)
library(lubridate)
library(stringr)
```

Originally, I wanted to do the final project on sexual assault at Harvard.
However, after speaking with the Title IX officer, I realized that this would be
very difficult. I asked the officer if she had the raw data for the AAU survey
(which contains most of the data I would be interested in), but she said even
she had difficulty accessing the Harvard data from AAU: she had to request it
from the data team at Harvard. Thus, it would be basically impossible for me to
access the data. I also looked for national data online, but this is also
heavily restricted. I decided that, given the difficulty, I would start over and
pick a new topic, unfortunately. With my interest in environmental science, I
decided I would switch to studying the meat industry (and possibly the new
Impossible Meat industry). The data was easier to obtain. I plan to examine (if
I can find the right data) how the Impossible Meat industry has disrupted meat
production.

```{r loading data, include=FALSE}

# Data from https://www.ers.usda.gov/data-products/livestock-meat-domestic-data/

meat <- read_excel("RedMeatPoultry_ProdFull.xlsx", skip = 2)

```

```{r clean data, include=FALSE}

# I am interested in how much meat is produced commercially, so I selected for
# the first 6 columns. The other columns deal with how much meat is federally
# inspected. Then I renamed the variables. The data had more than one
# observation per row, so I pivoted the data to make it neater. I also wanted to
# ignore the NAs. I reorganized the order of the variables. The top and tail end
# of the data were irrelevant, so I removed them from the dataset. I then wanted
# to look at how much meat prodcution has grown per decade.

meat_clean <- meat %>% 
  select(1:6) %>% 
  rename(beef = "Beef 3/...2") %>% 
  rename(veal = "Veal 3/...3") %>% 
  rename(pork = "Pork 3/...4") %>% 
  rename("lamb and mutton" = "Lamb and mutton 3/...5") %>% 
  rename(date = "...1") %>% 
  rename(total = "Total red meat 3/ 4/...6") %>% 
  pivot_longer(cols = 2:5, names_to = "kind_of_meat") %>% 
  rename(red_meat_produced = value) %>% 
  filter(!is.na(red_meat_produced) | !is.na(total))
meat_clean = meat_clean[,c(1,3,4,2)]
meat_clean = meat_clean[-c(1:8, 1773:2905),]

meat_clean_decade <- meat_clean[c(5:52, 485:532, 965:1012, 1445:1492),] 

```

```{r create graph, echo=FALSE}

# The issue with this graph is that the dates on the x-axis are out of numerical
# order. I tried to fix this at first my changing the "date" variable to a class
# of date using as.Date; however, when I attempted that, it returned only NAs. I
# then tried to parse the dates using parse_date using the lubridate package,
# but it returned an error where it says that the date variable is not in the
# class of character, even though it already is. I was unsuccessful in turning
# the variable into a class of date. I then changed the variable into a factor
# so I could use fct_relevel like we did in one of the PSETs to reorder the
# levels, but that did not work because "date" only yieled one level. I was
# unsuccessful in changing the order of the x-axis labels, but if it were
# ordered correctly, I hypothesize that I would see growth in meat production. I
# tried scaling by log_10 as well, but the graph looked better without the log
# scale.

meat_clean_decade %>% 
  ggplot() + 
  geom_point(aes(x = date, y = red_meat_produced, color = kind_of_meat)) +
  labs(title = "Red Meat Produced From 1989 - 2019",
       x = "Date",
       y = "Red Meat Produced (Millions of Pounds)", 
       color = "Kind of Meat") +
       theme_classic() +
      theme(
        legend.position = "right",
        axis.text.x = element_text(angle = 80, hjust = 1))

```
